Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-03-11 paper/paper1/ms.tex
Major surgery on the paper, closes #20, for now

We start with a high resolution pre-computed synthetic stellar model spectrum, $\mathsf{S}(\bm{\lambda})$. The procedure is largely agnostic to the exact details of how this spectrum was made. For the purposes of this paper, we will showcase examples from two well-known families of precomputed synthetic spectra: \texttt{PHOENIX} \citep{husser13} for stellar spectra $(T_{\mathrm{eff}}\in [2300, 10000]\;K)$ and \texttt{Sonora} \citep{2021ApJ...920...85M} for brown dwarf spectra $(T_{\mathrm{eff}}\in [1000, 2300]\;K)$. We place the following demands on the precomputed spectra. They should have sporadic regions of discernable continuum devoid of lines, and the continuum must vary smoothly in wavelength. The spectral lines or pseudo-lines should be resolved, and not sub-sampled. We suspect most stellar spectra meet these criteria, except for the coolest M dwarfs and brown dwarfs. The method can hypothetically handle spectra without discernable continua, but we suspect some modifications to the preprocessing steps would be needed. We truncate the red and blue limits of the precomputed synthetic spectrum to match a high-bandwidth echelle spectrograph, extended with a buffer at the edges of size $\pm \Delta \lambda_{\mathrm{buffer}}$, chosen to account for plausible radial velocity and rotational broadening of real stars. A generous buffer of $v \sin{i} < 500 \;\kmps$ and $|RV|<500 \;\kmps$ yields a typical buffer of about 30~\AA.

The choice of limiting the bandwidth to a region-of-interest around a single echelle spectrograph bandwidth stems from computational constraints. In principle, there is no fundamental limit to the bandwidth one could clone with the method presented here, up to and including the entire precomputed synthetic spectral model bandwidth. We adopt the exact native wavelength sampling with no smoothing or interpolation, yielding a wavelength vector $\bm{\lambda}_s$ with length $N_\mathrm{s}$ equal to the number of pixels within the extents of our region of interest including the buffers.

@@

We initialize the cloned model with a series of preprocessing steps. We divide the entire spectrum by a black body of the same effective temperature $T_{\mathrm{eff}}$ as the model template. The resulting signal typically possesses a smooth continuum variation. An additional continuum flattening step ensures that subsequent spectral line finding steps get applied uniformly. Here, we identify the continuum regions by the most prominent peaks in the specturm separated by a distance of at least 5,000$-$90,000 pixels from adjacent peaks, yielding between 60 and 5 control points. We then fit an $n_{\mathrm{poly}} = 3^{rd}-15^{th}$ order polynomial to these peaks, evaluate the polynomial on the entire bandwidth $\mathsf{P}(\bm{\lambda}_s)$, and divide the spectrum by this trend. Visual inspection of this continuum-flattened spectrum typically possesses variations at the $<1\%$ level. Tuning the pixel distance and polynomial order can lower the undulations to $<0.05\%$ level for some input spectra. We found a pixel distance of 50,000 and $3^{rd}$ order polynomial worked across the range of effective temperatures for HPF's bandwidth. The IGRINS spectra had more significant continuum opacity and band heads to accommodate and therefore needed to capture finer-scale variation: 5,000 pixels and a $9^{th}$ order polynomial appeared adequate over most of the effective temperature range.

@@

We emphasize that a recreation of the unvarnished input spectrum can be obtained by multiplying the continuum-flattened signal by the ``perturbed black body'', $\mathsf{B}(\bm{\lambda}_s)\cdot \mathsf{P}(\bm{\lambda}_s)$, that symbolizes the black body modulated by continuum opacity or broad-band radiative transfer effects. This smooth spectrum may be useful for applications that need to keep track of broad-band flux, such as low-resolution spectra, or regions with molecular band heads. The ``perturbed black body'' continuum model contains $n_{\mathrm{poly}}+1$ fixed-but-possibly tunable lookup parameters, plus the fixed input $T_{\mathrm{eff}}$.

Next, we identify the spectral lines. We apply a local-minimum-finding algorithm on the spectrum by defining a prominence threshold $P_{rom} \in (0.005, 0.02)$. This threshold dictates the number of lines that will be modeled: a lower prominence finds more, weaker lines, and a larger prominence finds fewer, deeper lines. The prominence algorithm successfully finds lines that reside on top of broad line wings, or unresolved band heads provided that the individual lines exceed the prominence threshold in their local region. The number of lines $N_{\mathrm{lines}}$ depends on the bandwidth, prominence, and the intrinsic properties of the input spectrum, principally effective temperature and metallicity.

For this paper, we illustrate examples for two \'echelle spectrographs with particularly large spectral grasp: the Habitable Zone Planet Finder \citep[HPF,][]{2014SPIE.9147E..1GM} on the Hobby-Eberly Telescope at McDonald Observatory in Fort Davis, Texas; and the Immersion Grating Infrared Spectrograph \citep[IGRINS,][]{park14}
currently on the Gemini South Telescope on Cerro Pach\'on in Chile. The $R=55,000$ HPF has a native bandwidth of $8079-12785$~\AA, which we expand to $8049-12815$~\AA~including the edge buffers. IGRINS has two cameras for $H$ and $K$ band, with the combined spectrum spanning $14267-25217\;$\AA~ including the edge buffers and the region in-between the two cameras, all at a resolving power of $(R=45,000)$. The spectrograph acquisition, reduction, and post-processing steps yield data $\mathsf{D}(\bm{\lambda}_{d})$, where $\bm{\lambda}_{d}$ is the wavelength vector at the instrumental resolution and sampling of each instrument, generally much coarser than the resolution and sampling grid of the precomputed synthetic spectra. The data wavelength vector may also contain gaps between \'echelle orders, whereas the precomputed wavelength coordinates are usually contiguous. HPF may have up to $2048\times28=$57,344 pixels, and IGRINS has typically about 75,000 pixels, after common trimming of noisy edge pixels and unusable telluric regions.

@@

Figure \ref{fig_Nlines_vs_teff} shows how the number of detected lines $N_{\mathrm{lines}}$ scales with effective temperature and prominence threshold $P_{rom}$ for the \texttt{PHOENIX} grid, truncated to the bandwidths-plus-buffers for HPF and IGRINS. We see between about 2,000 and 20,000 lines depending on the $T_{\mathrm{eff}}$ and $P_{rom}$. HPF and IGRINS have a comparable number of lines, and halving the prominence increases the number of lines by about $20-30\%$ in these ranges. The number of lines monotonically increases towards cooler effective temperatures.
The HPF-truncated spectra have $N_s=$335,849 native resolution samples, comparable to the IGRINS-truncated spectra, $N_s=$330,052.

@@

We have now arrived at the \emph{blas\'e} clone model $\mathsf{M}(\bf{\lambda}_s)$ for a flattened synthetic spectrum $\mathsf{S}$: it is the cumulative product of transmission through the sea of all overlapping spectral lines:

\begin{eqnarray}
    \mathsf{M}(\bm{\lambda}_s) = {\displaystyle \mathsf{P} \prod_{j=1}^{N_{\mathrm{lines}}} (1-a_j \mathsf{V}(\bm{\lambda}_s-\lambda_{c,j}, \sigma_j, \gamma_j) )} \label{equation1}
\end{eqnarray}

where $\mathsf{V}(\lambda, \sigma_j, \gamma_j)$ is the normalized Voigt profile with Gaussian standard deviation $\sigma$, Lorentzian half-width $\gamma$, at line center position $\lambda_c$, for the $j^{th}$ spectral line. The amplitude $a$ is always expected to be positive for absorption lines and is equal to the area under the curve of the line since the Voigt profile is normalized. The optional Prefactor term $\mathsf{P}$ is fixed at $1$ by default but can be allowed to vary to fine-adjust imperfections leftover from the polynomial-based continuum flattening procedure.

\subsection{Voigt profile evaluation}
The Voigt profile $\mathsf{V}(\lambda, \sigma_j, \gamma_j)$ can be computed in exact closed-form using the Voigt-Hjerting function \citep{1938ApJ....88..508H} as the real part of the complex Fadeeva function \citep[\emph{e.g.}][]{2011arXiv1106.0151Z}. Evaluation of the Fadeeva function can be computationally costly, and so approximate forms may be desirable. Here we adopt the pseudo-Voigt approximation \citep{Ida:nt0146}.

Two sampled Voigt approaches could be feasible. Direct convolution of a sampled Gaussian and Lorentzian profile may be too costly and inexact if pixels are coarsely sampled. Analogously, the convolution can be achieved in the Fourier domain through the multiplication of the Fast Fourier Transforms of the Gaussian and Lorentzian profiles, followed by the subsequent Inverse Fourier Transforms. The main rationale for either of these two choices would be to anticipate and align with planned convolutions such as rotational broadening and instrumental kernels. We do not currently implement these sampled convolutions in \emph{blas\'e} due to their prohibitive computational cost.

@@

\subsection{Goodness of fit metric}
The model evaluated with its coarse initial values would have terrible performance: it would only vaguely resemble the synthetic spectral model, with up to $\pm 50\%$ undulations from the inexact assignment of widths, lineshapes, and amplitudes. Instead, we tune the parameters of the model, starting from these coarse initial values. This model has $N_{\mathrm{lines}}\times 3$ free parameters, where the center wavelength is held fixed and the amplitude, width, and lineshape are allowed to vary. We minimize a scalar ``goodness-of-fit'' metric, \emph{aka} loss scalar $\mathcal{L}$, chosen as the mean squared error (MSE), which is proportional to $\chi^2$, the sum of the squares of the residual vector $\mathsf{R} \equiv \mathsf{S}-\mathsf{M}$ but has no notion of per-pixel noise since the precomputed synthetic spectrum has no uncertainty:

\begin{eqnarray}
    \mathcal{L} = \sum_i^{N_s} (S_i - M_i)^2 = \mathsf{R^\intercal}\cdot \mathsf{R}
\end{eqnarray}

As seen in Figure \ref{fig_Nlines_vs_teff}, the number of lines can exceed 7,000, meaning the model has over 7,000 $\times 3 =$ 21,000 free parameters. Fitting that large number of parameters is difficult with conventional optimizers, which struggle to converge after hundreds of parameters\authorcomment1{Citation to limits of optimizers}.

Here we employ a variant of Stochastic Gradient Descent (SGD), an optimization technique that can scale to a virtually unlimited number of parameters\authorcomment1{provide a citation}. This technique computes the derivative of the loss scalar with respect to each of the parameters, the Jacobian: $(\frac{\partial \mathcal{L}}{\partial a_j}, \frac{\partial \mathcal{L}}{\partial \sigma_j}, \frac{\partial \mathcal{L}}{\partial \gamma_j})$. The Jacobian indicates how the MSE would decrease with a change in the parameter-of-interest, or put simply which-way and by-how-much you have to change the line properties to get a better fit.

@@

In principle, we could compute the Jacobians analytically---since the partial derivatives of the Voigt function are known in closed-form---circumventing the vendor lock-in and memory overhead of an autodiff implementation with PyTorch. Further, an autodiff-aware implementation of the \emph{celerit\'e} algorithm \citep{2017AJ....154..220F} does not yet exist in PyTorch, constricting our choices for simultaneous continuum fitting. In practice, PyTorch also offers hardware acceleration on GPU or TPU \citep{10.1145/3079856.3080246}, mature support for a range of optimizers, and other perks that motivated its choice over analytic implementations or other machine learning frameworks. The GPyTorch framework \citep{2018arXiv180911165G} may offer a workaround to the absence of a \emph{celerit\'e} implementation. Still, the performance of an analytic Jacobian implementation over the autodiff route presented here offers an interesting avenue of future research.

@@

We set the \texttt{requires\_grad=True} property for any Torch tensor that we want to vary. This allows us to easily explore whether, say, allowing the $\lambda_c$ parameter to vary significantly improves the fit. It also allows us to tune or freeze an experimental wavelength-dependent pre-factor to Equation \ref{equation1} to correct for lingering imperfections in the otherwise-fixed continuum flattening procedure.

The computational bottleneck occurs at the evaluation of Equation \ref{equation1}, which includes the assembly of a $N_{\mathrm{lines}}\times N_{s}$ matrix $\bm{\bar{V}}$ assembled by stacking each Voigt profile $\mathsf{V}_j(\bm{\lambda}_s)$ on top of each other:

\begin{equation}
    \begin{pmatrix}
        \mathsf{V}_1(\bm{\lambda}_s)                    & \\
        \mathsf{V}_2(\bm{\lambda}_s)                    & \\
        \vdots                                          & \\
        \mathsf{V}_{N_{\mathrm{lines}}}(\bm{\lambda}_s) &
    \end{pmatrix}
\end{equation}

Equation \ref{equation1} performs a matrix contraction, turning a $N_{\mathrm{lines}}\times N_{s}$ matrix into a $1\times N_{s}$ vector. The number of Floating Point Operations (FLOPS) scales with the number of entries in this matrix, with a scalar prefactor for the cost of evaluating a single line profile at a single wavelength point. Efficient GPU algorithms exist for tensor contractions such as this product along an axis of a matrix, allowing this computation to proceed quickly on modern machines\authorcomment1{add citation?}. In particular, the proprietary CUDA architecture for NVIDIA\textsuperscript{\tiny\textregistered} GPUs contains Tensor cores with specialized matrix math, although the algorithms place restrictions on floating precision depending on the particular hardware and software available. The chief bottleneck occurs when the storage of the $\bm{\bar{V}}$ matrix exceeds the available RAM of a GPU or CPU: the computation will fail with an ``Out of Memory'' exception. Modern NVIDIA GPUs have $8-40$ GB of RAM. The memory bottleneck is even more pernicious than mere storage of the $\bm{\bar{V}}$ matrix since the CPU/GPU also has to store the computation graph for autodiff. The computation graph takes up more memory than the matrix itself, so it is generally not possible to evaluate Equation \ref{equation1} in its entirety in one-fell-swoop. A remedy is needed.

\subsection{Minibatches}

@@

The first, and expected, source of large residuals is simply missing line opacity due to our finite prominence threshold. Lines with prominence less than $P_{rom}$ yield residual notches with strengths comparable to $P_{rom}$. Including smaller prominence lines by lowering $P_{rom}$ produces smaller residuals, at the tradeoff of computing more lines and yielding higher computational cost.  But at some point, turning down $P_{rom}$ yields diminishing returns, as other imperfections provide a noise floor.  We have experimentally determined this noise floor to occur near $P_{rom}=0.01$.

@@

>>>>

We start with a high resolution pre-computed synthetic stellar model spectrum, $\mathsf{S}_{\rm abs}(\bm{\lambda})$ at its native resolution sampling and with its original absolute physical flux units. The procedure that follows is largely agnostic to the exact details of how this spectrum was made, or what physics or chemistry it may represent. For the purposes of this paper, we will showcase examples from two well-known families of precomputed synthetic astronomical spectra: \texttt{PHOENIX} \citep{husser13} for stellar spectra $(T_{\mathrm{eff}}\in [2300, 10000]\;K)$ and \texttt{Sonora} \citep{2021ApJ...920...85M} for brown dwarf spectra $(T_{\mathrm{eff}}\in [1000, 2300]\;K)$. The framework may also work for precomputed synthetic spectra of exoplanets, supernovae, galaxies, or even further afield such as laboratory physical chemistry.  We place the following demands on the precomputed spectra. They should have sporadic regions of discernable continuum devoid of lines, and the continuum must vary smoothly in wavelength. The spectral lines or pseudo-lines should be resolved, and not sub-sampled. We suspect most stellar spectra meet these criteria, except for the coolest M dwarfs and brown dwarfs. The method can hypothetically handle spectra without discernable continua, but we suspect some modifications to the preprocessing steps would be needed. We truncate the red and blue limits of the precomputed synthetic spectrum to match a high-bandwidth echelle spectrograph, extended with a buffer at the edges of size $\pm \Delta \lambda_{\mathrm{buffer}}$, chosen to account for plausible radial velocity and rotational broadening of real stars. A generous buffer of $v \sin{i} < 500 \;\kmps$ and $|RV|<500 \;\kmps$ yields a typical buffer of about 30~\AA.

The choice of limiting the bandwidth to a region-of-interest around a single echelle spectrograph bandwidth stems from computational constraints. In principle, there is no fundamental limit to the bandwidth one could clone with the method presented here, up to and including the entire precomputed synthetic spectral model bandwidth. We adopt the exact native wavelength sampling with no smoothing or interpolation, yielding a wavelength vector $\bm{\lambda}_S$ with length $N_\mathrm{S}$ equal to the number of pixels within the extents of our region of interest including the buffers.

@@

We initialize the cloned model with a series of preprocessing steps. We divide the entire spectrum by a black body $\mathsf{B}(\bm{\lambda}_S)$ of the same effective temperature $T_{\mathrm{eff}}$ as the model template. The resulting signal typically possesses a smooth continuum variation. An additional continuum flattening step ensures that subsequent spectral line finding steps get applied uniformly. Here, we identify the continuum regions by the most prominent peaks in the specturm separated by a distance of at least 5,000$-$90,000 pixels from adjacent peaks, yielding between 60 and 5 control points. We then fit an $n_{\mathrm{poly}} = 3^{rd}-15^{th}$ order polynomial to these peaks, evaluate the polynomial on the entire bandwidth $\mathsf{P}(\bm{\lambda}_S)$, and divide the spectrum by this trend. The result should be a flattened ``continuum-normalized'' spectrum familiar to practitioners in high resolution spectroscopy, with the continuum level close to unity.  It is this spectrum that will serve as the centerpiece of subsequent training steps.  We therefore drop any subscript and simply refer to this flattened spectrum as $\mathsf{S}$:

\begin{eqnarray}
    %\mathsf{S} = \frac{\mathsf{S}_{\rm abs}}{\mathsf{B} \; \mathsf{P}}
    \mathsf{S} = \mathsf{S}_{\rm abs}/\mathsf{B} / \mathsf{P}
\end{eqnarray}

where the division indicates element-wise division of these arrays or ``vectors'' of flux values.  Visual inspection of this continuum-flattened spectrum typically possesses variations at the $<1\%$ level. Tuning the pixel distance and polynomial order can lower the undulations to $<0.05\%$ level for some input spectra. We found a pixel distance of 50,000 and $3^{rd}$ order polynomial worked across the range of effective temperatures for HPF's bandwidth. The IGRINS spectra had more significant continuum opacity and band heads to accommodate and therefore needed to capture finer-scale variation: 5,000 pixels and a $9^{th}$ order polynomial appeared adequate over most of the effective temperature range.

@@

We emphasize that a recreation of the unvarnished input spectrum can be obtained by multiplying the continuum-flattened signal by the ``perturbed black body'', $\mathsf{B}(\bm{\lambda}_S)\odot \mathsf{P}(\bm{\lambda}_S)$, that symbolizes the black body modulated by continuum opacity or broad-band radiative transfer effects. This smooth spectrum may be useful for applications that need to keep track of broad-band flux, such as low-resolution spectra, or regions with molecular band heads. The ``perturbed black body'' continuum model contains $n_{\mathrm{poly}}+1$ fixed-but-possibly tunable lookup parameters, plus the fixed input $T_{\mathrm{eff}}$.

Next, we identify the spectral lines. We apply a local-minimum-finding algorithm on the spectrum by defining a prominence threshold $P_{\rm rom} \in (0.005, 0.02)$. This threshold dictates the number of lines that will be modeled: a lower prominence finds more, weaker lines, and a larger prominence finds fewer, deeper lines. The prominence algorithm successfully finds lines that reside on top of broad line wings, or unresolved band heads provided that the individual lines exceed the prominence threshold in their local region. The number of lines $N_{\mathrm{lines}}$ depends on the bandwidth, prominence, and the intrinsic properties of the input spectrum, principally effective temperature and metallicity.

For this paper, we illustrate examples for two \'echelle spectrographs with particularly large spectral grasp: the Habitable Zone Planet Finder \citep[HPF,][]{2014SPIE.9147E..1GM} on the Hobby-Eberly Telescope at McDonald Observatory in Fort Davis, Texas; and the Immersion Grating Infrared Spectrograph \citep[IGRINS,][]{park14}
currently on the Gemini South Telescope on Cerro Pach\'on in Chile. The $R=55,000$ HPF has a native bandwidth of $8079-12785$~\AA, which we expand to $8049-12815$~\AA~including the edge buffers. IGRINS has two cameras for $H$ and $K$ band, with the combined spectrum spanning $14267-25217\;$\AA~ including the edge buffers and the region in-between the two cameras, all at a resolving power of $(R=45,000)$. The spectrograph acquisition, reduction, and post-processing steps yield data $\mathsf{D}(\bm{\lambda}_{D})$, where $\bm{\lambda}_{D}$ is the wavelength vector at the instrumental resolution and sampling of each instrument, generally much coarser than the resolution and sampling grid of the precomputed synthetic spectra. The data wavelength vector may also contain gaps between \'echelle orders, whereas the precomputed wavelength coordinates are usually contiguous. HPF may have up to $2048\times28=$57,344 pixels, and IGRINS has typically about 75,000 pixels, after common trimming of noisy edge pixels and unusable telluric regions.

@@

Figure \ref{fig_Nlines_vs_teff} shows how the number of detected lines $N_{\mathrm{lines}}$ scales with effective temperature and prominence threshold $P_{\rm rom}$ for the \texttt{PHOENIX} grid, truncated to the bandwidths-plus-buffers for HPF and IGRINS. We see between about 2,000 and 20,000 lines depending on the $T_{\mathrm{eff}}$ and $P_{\rm rom}$. HPF and IGRINS have a comparable number of lines, and halving the prominence increases the number of lines by about $20-30\%$ in these ranges. The number of lines monotonically increases towards cooler effective temperatures.
The HPF-truncated spectra have $N_s=$335,849 native resolution samples, comparable to the IGRINS-truncated spectra, $N_s=$330,052.

@@

We have now arrived at the \texttt{blas\'e} clone model $\mathsf{S}_{\rm clone}(\bf{\lambda}_s)$ for a flattened synthetic spectrum $\mathsf{S}$: it is the cumulative product of transmission through the sea of all overlapping spectral lines:

\begin{eqnarray}
    \mathsf{S}_{\rm clone} = {\displaystyle \prod_{j=1}^{N_{\mathrm{lines}}} 1-a_j \mathsf{V}_j } \label{equation1}
\end{eqnarray}

where $\mathsf{V}_j$ is the Voigt profile $\mathsf{V}(\bm{\lambda}_S-\lambda_{\mathrm{c},j}, \sigma_j, \gamma_j)$ with Gaussian standard deviation $\sigma$, Lorentzian half-width $\gamma$, at line center position $\lambda_c$, for the $j^{th}$ spectral line. The amplitude $a$ is always expected to be positive for absorption lines.

The Voigt profile $\mathsf{V}(\lambda, \sigma_j, \gamma_j)$ can be computed in exact closed-form using the Voigt-Hjerting function \citep{1938ApJ....88..508H} as the real part of the complex Fadeeva function \citep[\emph{e.g.}][]{2011arXiv1106.0151Z}. Evaluation of the Fadeeva function can be computationally costly, and so approximate forms may be desirable. Here we adopt the pseudo-Voigt approximation \citep{Ida:nt0146}.

@@

\subsection{Goodness of fit metric}
The model evaluated with its coarse initial values would have terrible performance: it would only vaguely resemble the synthetic spectral model, with up to $\pm 50\%$ undulations from the inexact assignment of widths, lineshapes, and amplitudes. Instead, we tune the parameters of the model, starting from these coarse initial values. This model has $N_{\mathrm{lines}}\times 3$ free parameters, where the center wavelength is held fixed and the amplitude, width, and lineshape are allowed to vary. We minimize a scalar ``goodness-of-fit'' metric, \emph{aka} loss scalar $\mathcal{L}$, chosen as the mean squared error (MSE), which is proportional to $\chi^2$, the sum of the squares of the residual vector $\mathsf{R} \equiv \mathsf{S}-\mathsf{S}_{\rm clone}$ but has no notion of per-pixel noise since the precomputed synthetic spectrum has no uncertainty:

\begin{eqnarray}
    \mathcal{L} = \sum_i^{N_S} (S_i - S_{\mathrm{clone},i})^2 = \mathsf{R^\intercal}\cdot \mathsf{R}
\end{eqnarray}

As seen in Figure \ref{fig_Nlines_vs_teff}, the number of lines can exceed 7,000, meaning the model has over 7,000 $\times 3 =$ 21,000 free parameters. Fitting that large number of parameters is difficult with conventional optimizers.  Here we employ a variant of Stochastic Gradient Descent (SGD), an optimization technique that can scale to a virtually unlimited number of parameters \citep{2016arXiv160904747R}. This technique computes the derivative of the loss scalar with respect to each of the parameters, the so-called \emph{Jacobian}: $(\frac{\partial \mathcal{L}}{\partial a_j}, \frac{\partial \mathcal{L}}{\partial \sigma_j}, \frac{\partial \mathcal{L}}{\partial \gamma_j})$. The Jacobian indicates how the MSE would decrease with a change in the parameter-of-interest, or put simply which-way and by-how-much you have to change the line properties to get a better fit.

@@

@@

The autodiff machinery has a convenient way to set which parameters are held fixed and which are iteratively fine-tuned.  One simply disables the Jacobian computations for the fixed parameters.  We set the \texttt{requires\_grad=True} property for any Torch tensor that we want to vary. This allows us to easily explore whether, say, allowing the $\lambda_\mathrm{c}$ parameter to vary significantly improves the fit.

The computational bottleneck occurs at the evaluation of Equation \ref{equation1}, which can be viewed as having a $N_{\mathrm{lines}}\times N_{S}$ matrix $\bm{\bar{V}}$ assembled by stacking each Voigt absoption profile $\mathsf{V}_j(\bm{\lambda}_s)$ on top of each other:

\begin{equation}
    \begin{pmatrix}
        1 -\mathsf{V}_1(\bm{\lambda}_s)                     & \\
        1 - \mathsf{V}_2(\bm{\lambda}_s)                    & \\
        \vdots                                              & \\
        1 - \mathsf{V}_{N_{\mathrm{lines}}}(\bm{\lambda}_s) &
    \end{pmatrix}
\end{equation}

Equation \ref{equation1} performs a type of matrix contraction, turning a $N_{\mathrm{lines}}\times N_{S}$ matrix into a $1\times N_{S}$ vector. The number of Floating Point Operations (FLOPS) scales with the number of entries in this matrix. Efficient GPU algorithms exist for matrix manipulations such as this one, allowing this computation to proceed quickly on modern machines. In particular, the proprietary CUDA architecture for NVIDIA\textsuperscript{\tiny\textregistered} GPUs contains Tensor cores with specialized matrix math. The chief bottleneck occurs when the storage of the $\bm{\bar{V}}$ matrix exceeds the available RAM of a GPU or CPU: the computation will fail with an ``Out of Memory'' exception. Modern NVIDIA GPUs have $8-40$ GB of RAM. The memory bottleneck is even more pernicious than mere storage of the $\bm{\bar{V}}$ matrix since the CPU/GPU also has to store the computation graph for autodiff. It is generally not possible to evaluate Equation \ref{equation1} in its entirety in one-fell-swoop. A remedy is needed.

@@

The first, and expected, source of large residuals is simply missing line opacity due to our finite prominence threshold. Lines with prominence less than $P_{\rm rom}$ yield residual notches with strengths comparable to $P_{\rm rom}$. Including smaller prominence lines by lowering $P_{\rm rom}$ produces smaller residuals, at the tradeoff of computing more lines and yielding higher computational cost.  But at some point, turning down $P_{\rm rom}$ yields diminishing returns, as other imperfections provide a noise floor.  We have experimentally determined this noise floor to occur near $P_{\rm rom}=0.01$.

@@

\subsection{Alternatives to the PseudoVoigt Profile}
Two sampled Voigt approaches could be feasible. Direct convolution of a sampled Gaussian and Lorentzian profile may be too costly and inexact if pixels are coarsely sampled. Analogously, the convolution can be achieved in the Fourier domain through the multiplication of the Fast Fourier Transforms of the Gaussian and Lorentzian profiles, followed by the subsequent Inverse Fourier Transforms. The main rationale for either of these two choices would be to anticipate and align with planned convolutions such as rotational broadening and instrumental kernels. We do not currently implement these sampled convolutions in \emph{blas\'e} due to their prohibitive computational cost.

\subsection{Prospects for closed-form computation of Jacobians}
In principle, we could compute the Jacobians analytically---since the partial derivatives of the Voigt function are known in closed-form---circumventing the vendor lock-in and memory overhead of an autodiff implementation with PyTorch. Further, an autodiff-aware implementation of the \emph{celerit\'e} algorithm \citep{2017AJ....154..220F} does not yet exist in PyTorch, constricting our choices for simultaneous continuum fitting. In practice, PyTorch also offers hardware acceleration on GPU or TPU \citep{10.1145/3079856.3080246}, mature support for a range of optimizers, and other perks that motivated its choice over analytic implementations or other machine learning frameworks. The GPyTorch framework \citep{2018arXiv180911165G} may offer a workaround to the absence of a \emph{celerit\'e} implementation. Still, the performance of an analytic Jacobian implementation over the autodiff route presented here offers an interesting avenue of future research.

\subsection{Tuning the continuum fit}
We could also tune or freeze an experimental wavelength-dependent pre-factor to Equation \ref{equation1} to correct for lingering imperfections in the otherwise-fixed continuum flattening procedure.

\subsection{What about minibatches?}
